

\section[FAQs]{FAQs}
\label{sec:faqs}
\addcontentsline{toc}{section}{\thesection. FAQs}


\subsection[General]{General}
\label{sec:general}
\addcontentsline{toc}{subsection}{\thesubsection. General}

\begin{enumerate}
\item {\bf\color{blue} Q:}
      Does \pkg{pbdRPC} support Windows system? \\
      {\bf\color{blue} A:}
      Yes, the \code{plink.exe} from PuTTY will be the program to send
      commands to remote servers. An internal built \code{plink.exe} will
      be provided and wrapped by the \pkg{pbdRPC} command \code{plink()}.

\item {\bf\color{blue} Q:}
      Is an authentication used in \pkg{pbdRPC}? How does it work? \\
      {\bf\color{blue} A:}
      Yes, the authentication is the same way to \code{ssh} and
      \code{plink.exe} provided public and private keys are setup correctly.
      For example, when an RSA key is used, the \code{ssh} will by
      default search
      \code{~/.ssh/id_rsa} or via the option ``\code{-i ./id_rsa}'' for a local
      private key.
      Similarly,
      the \code{plink.exe} uses the option ``\code{-i ./id_rsa.ppk}'' for a
      local private key.
      Inside \pkg{pbdRPC}, one can use the options of the control
      \code{.pbd_env$RPC.LI$priv.key} and \code{.pbd_env$RPC.LI$pri.key.ppk} to
      indicate the file of the private key. Then, \code{ssh()}, \code{plink()},
      and \code{srpc()} commands will automatically access those files,
      accordingly.

\item {\bf\color{blue} Q:}
      Can a \code{ssh} private key be converted to \code{plink}'s private
      key? i.e. convert OpenSSH format to PuTTY format. \\
      {\bf\color{blue} A:}
      Yes, the \code{puttygen} on linux can convert the \code{id_rsa}
      (OpenSSH format) to \code{id_rsa.ppk} (PuTTY format) as the commands
      below.
\begin{Command}
$ sudo apt-get install putty
$ puttygen id_rsa -O private -o id_rsa.ppk
\end{Command}

\item {\bf\color{blue} Q:}
      Is it possible to capture the returns from the RPC calls
      by \code{srpc()}, \code{ssh()}, or \code{plink()}? How? \\
      {\bf\color{blue} A:}
      Yes, set the arguments \code{intern = TRUE} and \code{wait = TRUE}
      to the RPC calls can obtain the outputs as used by \code{system()}.
      The \code{plink()} used in \code{RGui} may not be able to capture
      the outputs unless the authentication is set because \code{shell.exec()}
      is used instead of \code{system()}.

\item {\bf\color{blue} Q:}
      Does \code{srpc()} support \code{SSH} (reverse/remote) tunneling or
      port forwarding? \\
      {\bf\color{blue} A:}
      Yes, theoretically there is no problem. However, there is no
      appropriate example to show that in \proglang{R}.
      See Sections~\ref{sec:arguments_local_port_forwarding}
      and \ref{sec:arguments_tunneling} for the command arguments.

\item {\bf\color{blue} Q:}
      Error messages from an \proglang{R} session or a shell/terminal
      are shown as the error below.
\begin{Error}
FATAL ERROR: Network error: Connection refused
\end{Error}
      or
\begin{Error}
ssh: connect to host 192.168.56.101 port 22: Connection refused
\end{Error}
      {\bf\color{blue} A:}
      The messages are mainly because of incorrect setups of SSH service.
      Check SSH service on remote servers.
      \begin{itemize}
      \item Install SSH server, such as the command below.
\begin{Command}
$ sudo apt-get install openssh-server
\end{Command}
      \item Check network, port, SSH service, and firewall configurations.
      \item Turn on connection permissions for SSH ports.
      \item Make sure password or authentication are correct.
      \end{itemize} 

\end{enumerate}

